Impact of engines scheduler on the performance of Big Data pipelines in HPC

### 2021-01-21 latex/paper.tex
[REVIEW] Methods section

\begin{IEEEkeywords}
	Performance, Scheduler, Big Data, Dask, Spark, Ray, Neuroimaging
\end{IEEEkeywords}
\MD{Discuss which keyword to use for the paper.}

@@

\subsection{Ray}

@@

\subsection{Applications}
\subsubsection{Increment}
We adapted the increment pipeline used in \cite{hayot2019performance}.
This synthetic application read blocks of the BigBrain from Lustre and sleeps for specified period.
To simulate intermediate results, we repeat the sleep process for a configurable amount of time.
We prevent data caching of the blocks by incrementing their voxels value by 1 after each sleep operation.
Finally, we write the resulting NIfTI image back to Lustre.
This application allow us the study engines when the inputs are processed independently.
The map-only scenario of this application mimics the processing of multiple independt subjects in parralel.
\MD{TODO: Add the Figure for the application graph.}

\subsubsection{Multi-Increment}
Our second application is a revision of the increment pipeline.
A major difference is that, at each iteration, a random BigBrain blocks is used to as the increment value.
This change allows the multi-increment application to have inter-worker communication while remaining simplistic.
\MD{TODO: Add the Figure for the application graph.}

\subsubsection{Histogram}
Our third application calculatest the histogram of the BigBrain image.
It reads the BigBrain blocks from Lustre, calculate frequency of each intensity, then write the aggregated result back on Lustre.
This map-reduce application has a very high read over write ratio.
Moreover, this application requires data shuffling; although little.
This place it in between the increment and multi-increment pipeline in terms of inter-worker communication.
\MD{TODO: Add the Figure for the application graph.}

\subsubsection{Kmeans} % TODO
\MD{TODO: Write about it once implemented.}

\subsubsection{BIDS app example}
Our last application is BIDS App example: a neuroimaging pipeline to extract brain volume.
For this application, the CoRR dataset was used.
It extracts the brain volume of each participant, then computes the average for each group of participants.
Unlike the other application, BIDS App example is a set of command-line distributed in a Docker image (bids/example on DockerHub).
We converted the Docker image to a Singularity image for use in HPC environment, \MD{Cite paper on reason why this is done.}
using \href{https://hub.docker.com/r/singularityware/docker2singularity/tags/}{docker2singularity}
\MD{Need to discuss if we preload the image on the worker nodes.}
\MD{TODO: Add the Figure for the application graph.}

>>>>

\begin{IEEEkeywords}
	Performance, Scheduler, Big Data, Dask, Spark, Neuroimaging
\end{IEEEkeywords}
\MD{Discuss which keyword to use for the paper.}

@@

@@

\subsection{Applications}
\subsubsection{Increment}
We adapted the increment pipeline used in \cite{hayot2019performance}.
This synthetic application reads blocks of the BigBrain from Lustre and simulates computation by sleeping for a specified period.
To simulate intermediate results, we repeat the sleep process for a configurable amount of time.
We prevent data caching of the blocks by incrementing their voxels value by one after each sleep operation.
Finally, we write the resulting NIfTI image back to Lustre.
This application allows us to study the engines when their inputs are processed independently.
The map-only scenario of this application mimics the processing of multiple independent subjects in parallel.
\MD{TODO: Add the Figure for the application graph.}

\subsubsection{Multi-Increment}
Our second application is a revision of the increment pipeline.
A significant difference is that, at each iteration, it uses a random BigBrain block as the increment value. 
This change allows the multi-increment application to have inter-worker communication while remaining simplistic.
\MD{TODO: Add the Figure for the application graph.}

\subsubsection{Histogram}
As our third application, we calculate the histogram of the BigBrain image. 
It reads the BigBrain blocks from Lustre, calculates each intensity's frequency, and then writes the aggregated result back on Lustre.
This map-reduce application has a very high read overwrite ratio.
Moreover, this application requires data shuffling, although little. 
The amount of inter-worker communication is in-between the increment and multi-increment pipelines.
\MD{TODO: Add the Figure for the application graph.}

\subsubsection{Kmeans} % TODO
For our fourth application, we use Kmeans to cluster the BigBrain image by voxel intensity.
We set the number of clusters to 3 to segment the white and grey matter and the noise.
The application starts by reading the image blocks, combining all voxels in a 1-D array, and choosing initial centroids using the min, max, and intermediate values.
It assigns each voxel to the centroids it is the closest and updates each centroid by computing the average of the voxels associated with it. 
It repeats the assignment and update steps for a configurable amount of time. 
Finally, the voxels of the image blocks are classified and write back on the file system.
Updating the centroids involves a lot of data communication between the worker.

Spark and Dask's implementation differs slightly for this application to take advantage of the" most suited" API from both engines.
Spark implementation uses the Map-Reduce paradigm, while Dask implementation uses array programming.
\MD{TODO: Add the Figure for the application graph.}

\subsubsection{BIDS app example}
Our last application is BIDS App example: a neuroimaging pipeline to extract brain volume.
For this application, we use the CoRR dataset.
It extracts the brain volume of each participant, then computes the average for each group of participants.
Unlike the other application, BIDS App example is a command-line set in a Docker image (bids/example on DockerHub).
We converted the Docker image to a Singularity image for use in HPC environments, \MD{Cite paper on reason why this is done.}
using \href{https://hub.docker.com/r/singularityware/docker2singularity/tags/}{docker2singularity}
\MD{Need to discuss if we preload the image on the worker nodes.}
\MD{TODO: Add the Figure for the application graph.}
